Making all equalities equal

### 2021-12-14 paper.lagda.tex
fixed grammar mistakes

The cubical flag is necessary because we are using cubical equality,
and the cumulativiy flag is also necessary for level subtyping,

@@

At the begin of Agda and in most theorems proves, equality is given by Martin-Löf's definition:

@@

The simplest example is the cubical equality hence this equality is already equal to itself.

@@

The proof of Martin-Löf equality is more difficult, but it is already in Cubical library as \AgdaFunction{p-c}.

@@

The isomorphism is an equality between types.

@@

\AgdaFunction{univalencePath} is already defined in Agda library, but with \AgdaBound{A ≃ B} instead of
\AgdaBound{Lifted (A ≃ B)}. This change can be done because of the cumulativity flag.

@@

The hardest equality to proof that is equalty is the Leibniz Equality.

@@

It is importing the definition of Leibniz equality made by \cite{abel2020leibniz}.
In this work, there is already a proof of the isomorphism between the Leibniz and the Martin-Löf equality.

@@

In Cubical Library, the definition of isomorphism uses cubical equality instead of Martin-Löf equality
when we have to proof that \AgdaBound{∀ x → from (to x) ≡ x} and \AgdaBound{∀ x → to (from x) ≡ x}.
\AgdaFunction{ptoc} is necessary to do this convertion from these equalities.

@@

Using the univalence and \AgdaFunction{liftIso} defined previously, it is possible to transform the isormorphism
into an equality.

@@

The equalities used previously were defined using the cubical equality.
Now I will define them using other equalities.

@@

I am importing a generic equality to use it to define a more generic equality.

@@

From a more generic defintion of equality,
it is easily possible to return to the less generic definition.

@@

Given a symmetric definition of the previous equality,
it is easy to prove that it is also an equality of type 2.

@@

In this part, a relation is an equality when it is equal (using a general equality) to a cubical equality.

@@

With this definition of equality, it is possible to prove that if an equality is equal to a cubical equality,
so it is equal (using the general or cubical equality) to the cubical equality.

@@

This is the proof that the symmetric definition of equality is also valid.

@@

It is possible to proof that a general equality is an equality from this definition:

@@

If there is a proof of the symmetrical equality, so it is also an equality from this definition:

@@

The best part of defining all of these stuffs is that it is now easy to proof that Leibniz equality is an equality.

>>>>

The cubical flag is necessary because we are using cubical equality,
and the cumulative flag is also necessary for level subtyping,

@@

At the beginning of Agda and in most theorems proves, equality is given by Martin-Löf's definition:

@@

The simplest example is cubical equality hence this equality is already equal in itself.

@@

The proof of Martin-Löf equality is more difficult, but it is already in the Cubical library as \AgdaFunction{p-c}.

@@

Isomorphism is equality between types.

@@

\AgdaFunction{univalencePath} is already defined in Agda library, but with \AgdaBound{A ≃ B} instead of
\AgdaBound{Lifted (A ≃ B)}. This change can be done because of the cumulative flag.

@@

The hardest equality to prove that is equality is the Leibniz Equality.

@@

It is importing the definition of Leibniz equality made by \cite{abel2020leibniz}.
In this work, there is already proof of the isomorphism between Leibniz and Martin-Löf equality.

@@

In Cubical Library, the definition of isomorphism uses cubical equality instead of Martin-Löf equality
when we have to prove that \AgdaBound{∀ x → from (to x) ≡ x} and \AgdaBound{∀ x → to (from x) ≡ x}.
\AgdaFunction{ptoc} is necessary to do this conversion from these equalities.

@@

Using the univalence and \AgdaFunction{liftIso} defined previously, it is possible to transform the isomorphism
into equality.

@@

The equalities used previously were defined using cubical equality.
Now I will define them using other equalities.

@@

I am importing generic equality to use it to define more generic equality.

@@

From a more generic definition of equality,
it is easily possible to return to the less generic definition.

@@

Given a symmetric definition of the previous equality,
it is easy to prove that it is also equality of type 2.

@@

In this part, a relation is equality when it is equal (using general equality) to cubical equality.

@@

With this definition of equality, it is possible to prove that if equality is equal to cubical equality,
so it is equal (using the general or cubical equality) to the cubical equality.

@@

This is proof that the symmetric definition of equality is also valid.

@@

It is possible to prove that a general equality is equality from this definition:

@@

If there is proof of symmetrical equality, so it is also equality from this definition:

@@

The best part of defining all of this stuff is that it is now easy to prove that Leibniz equality is equality.
